---
title: "02-model"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 999)
library(tidyverse)
library(modeldata)
library(tidymodels)

data("ad_data")
alz <- ad_data
print("Hello Italy!")
```

# Your Turn 1

Run the chunk below and look at the output. Then, copy/paste the code and edit to create:

+ a decision tree model for classification 

+ that uses the `C5.0` engine. 

Save it as `tree_mod` and look at the object. What is different about the output?

*Hint: you'll need https://www.tidymodels.org/find/parsnip/*

```{r}
lr_mod <- 
  logistic_reg(engine = "glm") %>% 
  set_mode("classification")
lr_mod
```

```{r}

```


# Your Turn 2

Fill in the blanks. 

Use `initial_split()`, `training()`, and `testing()` to:

1. Split **alz** into training and test sets. Save the rsplit!

2. Extract the training data and testing data.

3. Examine the proportions of the Class variable in each. 

Keep `set.seed(100)` at the start of your code.

*Hint: Be sure to remove every `_` before running the code!*

```{r}
set.seed(100) # Important!

alz_split  <- ________(alz, strata = Class, prop = .9)
alz_train  <- ________(alz_split)
alz_test   <- ________(alz_split)

```


## Your Turn 3

Run the code below. What does it return?

```{r}
set.seed(100)
alz_folds <- 
    vfold_cv(alz_train, v = 10, strata = Class)
alz_folds
```
